---
title: "Project 3 Instructions"
author: ""
date: "Updated Dec 30 [Updates Coming]"
output: 
  html_document:
    code_folding: hide
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```


# Project Outline
This project outline and background information have been provided to assist you as you complete your project. You should assume the reader of your work has no knowledge or access to this information.

How much explosive material remains in the soil? The military is concerned about amount of explosives that remain in the soils of training ranges because soldiers are out on the training range and explosive residues are carcinogens. Collecting a representative sample from the training ranges is difficult to do and scientists continue working on developing, refining, and validating sampling methods. [Source](https://serdp-estcp.org/content/download/5167/73264/file/ER-0628-FR.pdf)

Our work in this project relies on assumptions and use of probability distributions. We will (1) fit probability distributions to data, (2) create simulated samples from those probability distributions, and (3) use the probability distributions to provide probability information about explosive residue in the surface soil of a training range.

Environment Protection Agency (EPA) specifies regulatory levels of Nitroglycerin concentrations for human heath. For this project, we will use 10 mg/kg[^note] as the toxicity threshold for surface soil of this training range.
[Source](https://cfpub.epa.gov/ncea/pprtv/documents/Nitroglycerin.pdf)



## Task 1: Data and General Models
- Create an R Markdown file.
- Use the code below to read in the soil data.
    ```{r load_libraries}
    # Use this R-Chunk to load all your libraries!
    
    # run this line once in the console to get package
        #devtools::install_github('byuidatascience/data4soils')
    library(data4soils)
    ```
    
    ```{r load_data, error=TRUE}
    # Use this R-Chunk to import all your datasets!

    #Ng <- cfbp_fpjuliet$ng
    ```
This code creates a vector called "Ng". The vector contains the measurements Nitroglycerin (Ng) in mg/kg found in 100 soil samples.

- Familiarize your self with the Nitroglycerin data.
  - Create a density histogram of the 100 Nitroglycerin measurements. 
  - Calculate the sample mean for these measurements. Use the command `?mean` in your Console to access the R documentation for the `mean()` command.
  - Calculate the sample standard variance for these measurements. Use the command `?var` in your Console to access the R documentation for the `var()` command.
- Consider the following general models
  - $f_0(m; a,b) = \frac{1}{b-a}$ with $-\infty < a < m < b < \infty$ (and 0 otherwise)  
This is called the uniform distribution. This is called the gamma distribution. Use the command `?dunif` or `?runif` in your Console to access the R documentation for the uniform distribution. The probability is the same (uniform) for all measurements between $a$ and $b$.
  - $f_1(m; \mu,\sigma) = \frac{1}{\sqrt{2\pi \sigma^2}}e^{-\frac{1}{2}\left(\frac{x-\mu}{\sigma}\right)^2}$ with $\mu > 0$, $\sigma > 0$, and $-\infty < m < \infty$  
This is called the normal distribution. Use the command `?dnorm` or `?rnorm` in your Console to access the R documentation for the normal distribution distribution. The probability a measurement is near $\mu$ is larger than the probability that a measurement is far from $\mu$. This distribution is symmetric and defined for all values of $m$.
  - $f_2(m; \alpha,\beta) =  \frac{\beta^{\alpha}}{\Gamma(\alpha)}m^{\alpha-1}e^{-\beta m}$ with $\alpha > 0$, $\beta >0$, and $m \geq 0$ (and 0 otherwise)  
This is called the gamma distribution. Use the command `?dgamma` or `?rgamma` in your Console to access the R documentation for the gamma distribution.
The function $\Gamma(x)$ is call the **gamma function** (NOT the gamma distribution). One way to think about the gamma function is a generalization of the factorial to noninteger values. Use the command `?gamma` in your Console to access the R documentation pages about the **gamma function**. 
  - $f_3(m; \lambda) =  \lambda e^{-\lambda m}$ with $\lambda > 0$ and $m \geq 0$ (and 0 otherwise)  
This is called the exponential distribution. Use the command `?dexp` or `?rexp` in your Console to access the R documentation for the exponential distribution. The exponential distribution is often thought of as a "waiting time" model.

- For each function, use the Desmos files below with sliders to dynamically explore how changing the parameter changes the behavior of the function.
  - [Desmos file for function 0](https://www.desmos.com/calculator/6snrwycie4)
  - [Desmos file for function 1](https://www.desmos.com/calculator/o2lb19ivnk)
  - [Desmos file for function 2](https://www.desmos.com/calculator/h03fdeh2ao)
  - [Desmos file for function 3](https://www.desmos.com/calculator/j8peg4jsy4)
- For each function, summarize your observations about the parameters in terms of transformations of functions (shifts, reflections, stretch) and the mathematical behavior of the function (increasing, decreasing, constant, positive, negative, nonnegative).
    - For each function, use the `plot()` commands in R to plot several representative curves illustrating what you learned in your parameter exploration. Use the `par(mfrow())` command to organize your plots into one figure.
- Organize your work into a **cohesive analysis** and submit it to Canvas.

## Task 2: Expected Value and Variance of **Stochastic Variables**
- Create a new R Markdown file.
- For each model (uniform distribution, normal distribution, gamma distribution, and exponential distribution) write down the definite integral required to calculate the expected value of the model. 
- Use Mathematica to compute the definite integrals (find the expected value of $f_0$, $f_1$, $f_2$ and $f_3$) as a function each model's parameters. 
- For each model (uniform distribution, normal distribution, gamma distribution, and exponential distribution) write down the definite integral required to calculate the variance of the model. 
- Use Mathematica to compute the definite integrals (find the variance of $f_0$, $f_1$, $f_2$ and $f_3$) as a function each model's parameters. 
- Organize your work into a **cohesive analysis** and submit it to Canvas.

## Task 3: Fit the Model ("Modified Method of Moments" Method)
- Create a new R Markdown file.
- Set the sample mean of the Nitroglycerin data equal to the expected value of $f_0$, set the sample variance of the Nitroglycerin data equal to the variance of $f_0$, and solve the system of equations for $a$ and $b$.
- Set the sample mean of the Nitroglycerin data equal to the expected value of $f_3$ and solve for $\lambda$.
- Write down each of the fitted models, $f_i(m)$ where $i = 0,1,2,3$ with the parameters values rounded to 3 decimal places as needed.
  - The computations for fitting $f_1$ and $f_2$ were completed in class (or provided to you).
  - Note when using fitted models it is best practice not to round in any preliminary calculations so make sure you use all known decimal places for the parameter values, NOT the rounded values, when you use the fitted model.
- Organize your work into a **cohesive analysis** and submit it to Canvas.

## Task 4: Use the Fitted Models to Answer Questions
- Create a new R Markdown file.
- What is the probability that the amount of explosive in a sample will be between 0 mg/kg and 5 mg/kg? Compute this probability for each of your four fitted models. Write down the integral you need to calculate and then use Mathematica to compute the integral.
- What is the probability that the amount of explosive in a sample will be more than 10 mg/kg? Compute the value for each of your four fitted models. Write down the integral you need to calculate and then use Mathematica to compute the integral.
- For $f_0$ and $f_3$ determine the 99$^{\text{th}}$ percentile of the distribution. Write down the equation you need to solve, it will include an integral, and then solve the equation.
- Use the `rexp()` and `rgamma()` commands in R with appropriate parameter values you found when you fit these distributions to the data to create a sample of 2500 random measurements using each fitted model.
- Use your simulated sample and adjust the code below to approximate how many samples out of 7500 will have more than 10 mg/kg of explosive when using the fitted gamma and exponential distributions.
  ```{r}
  #tmp1 <- rexp(7500, rate = lambda)
  #length(which(tmp1 > 10))
  
  #tmp2 <- rgamma(7500, shape = alpha, rate = beta)
  #length(which(tmp2 > 10))  
  ```
- Using the fitted gamma and expnential distributions simulated data, calculate the probability that a sample will have an more than 10 mg/kg of explosive.
- Describe in 4-6 sentences how the information you get from the data depends on the general model you assume. Why is this an important concept to understand when working with models and data?
- Are any of your fitted models inconsistent with the story the data tells in the density histogram of the Nitroglycerin in the soil?
    - If a fitted model is inconsistent with what we know about a situation, it is suspect and suggests further work should be done before trusting that model or it should not be used as a model in that situation.
- Organize your work into a **cohesive analysis** and submit it to Canvas.

## Project 3: Bringing it All Together
- Create a new R Markdown file.
- Organize your work from Tasks 1-4 into a **cohesive analysis** and submit it to Canvas. Use only the important and relevant plots, calculations, and information.
    - Begin with background and an introduction to the question(s) you will be answering with the soil data.
- Reflect on your work for this project. At the bottom of your report include the following in a brief (1-2 paragraph) reflection.
    - Identify/explain 2-3 key mathematical  ideas you learned (and would like to remember).
    - Identify/explain 1-3 soft skills you needed/improved/learned while working on the project.
        - List of some Soft Skills
            - Dedication
            - Following Directions
            - Motivation
            - Self-directed
            - Organization
            - Planning
            - Time Management
            - Willing to Accept Feedback
            - Perseverance
            - Good attitude
            - Meets deadlines
            - Willingness to learn



[^note]: This number is a simplified story for illustrative purposes only.