\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{xcolor}
\usepackage{hyperref}

\usepackage{rotating}

\usepackage{tabls}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{multicol}
\usepackage{enumitem}
\usepackage{microtype}
\usepackage{tikz}
\usepackage{pgfplots}
\usetikzlibrary{positioning}
\usepackage{multirow}

\usepackage{comment}

\usepackage{graphicx}
\usepackage{wrapfig}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem*{theorem*}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem*{lemma*}{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}

\theoremstyle{box}
\newtheorem{definition}[theorem]{Definition}
\newtheorem*{axiom*}{Axiom}
\newtheorem{dfn}[theorem]{Definition}
\newtheorem*{definition*}{Definition}
\newtheorem*{exercise*}{Exercise}
\newtheorem{observation}[theorem]{Observation}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{example}[theorem]{Example}
\newtheorem{question}[theorem]{Question}
\newtheorem*{prep-problems}{Preparation Problems}

\newcommand{\pd}[3]{\frac{\partial^{#3} {#1}}{\partial {#2}^{#3}}}
\newcommand{\fpd}[2]{\frac{\partial {#1}}{\partial {#2}}}
\newcommand{\diff}[2]{\frac{d {#1}}{d {#2}}}


\begin{document}
\section{Objectives}
\begin{itemize}
\item Calculate basic discrete probabilities.
	\begin{itemize}
	\item Compute the probability of equally likely events.
	\item Compute the probability of the intersection of two events.
	\item Compute the probability of the union of two events.
	\item Compute conditional probabilities.
	\end{itemize}
\item Use definitions to learn about and communicate mathematical ideas.
	\begin{itemize}
	\item Recognize independent events.
	\item Recognize mutually exclusive events.
	\end{itemize}
\item Write down the pmf for some discrete random variables.
\item Use the pmf to calculate probability.
\end{itemize}
\subsection{Resources:}
\subsection{Announcements:}
\begin{itemize}
\item I have pushed the due date for Project 1 to Oct. 14.
\item I will be changing the due date for the ``1 -- Discrete Probability \& Expected Value" Knewton Alta assignment.
\item A word about the Project and units. (percent\_intensity column, histograms we will talk about this in the next couple days when we talk about histograms)
\item Common misunderstanding... Given $f(x) = 3x-14$, what does the symbol $f(x) = 2$ mean? (In case you are wondering did we ever talk about this in class, the answer is YES. We talked about this on Tuesday last week during our ``Practice with Exponential Function". One of the things that have been demonstrated over our work the last several weeks is that function notation is NOT dependent on the type of function. -- remember our work with the general transformation)
\end{itemize}

%\subsection{table of contents}

\newpage
\section{Agenda}
\subsection{Probability}

\subsubsection{Examples}
Consider an experiment where we roll a 6-sided die once. The \textbf{sample space} in this case is $\Omega = \{1,2,3,4,5,6\}$.
\begin{itemize}
\item Let $A$ be the event the outcome is odd and $B$ be the event the outcome is greater than 3.\\
Thus $A = \{1,3,5\}$ and $B = \{4,5,6\}$. Calculate the following:
\begin{itemize}
\item $P(A)$
\item $P(B)$
\item $P(A \cap B)$
\item $P(A \cup B)$\\
Method 1 -- make a list and count\\
Method 2 -- more general approach, $P(A \cup B) = P(A) + P(B) - P(A \cap B)$
\item $P(A|B)$
\item $P(B|A)$
\end{itemize}
Notice: $P(A \cap B) \neq  0$ so $A$ and $B$ are NOT mutually exclusive.\\
Notice: $P(A|B) \neq P(A)$ so $A$ and $B$ are NOT independent.\\
Note: In this example $P(A|B) = P(B|A)$ is this always true? No. (See next example.)

\item Let $A$ be the event the outcome is less than 5 and $B$ be the event the outcome is even.\\
Thus $A = \{1,2,3,4\}$ and $B = \{2,4,6\}$. Calculate the following:
\begin{itemize}
\item $P(A)$
\item $P(B)$
\item $P(A \cap B)$\\
Notice: $P(A \cap B) \neq 0$ so $A$ and $B$ are NOT mutually exclusive.\\
Notice The set $(A \cap B)$ has no elements. We write that $(A \cap B) = \emptyset$.\\
\begin{definition*}[Disjoint Sets]
If the intersection of two sets is the empty set, we say the sets are disjoint.
\end{definition*}
\item $P(A \cup B)$\\
Notice: $P(A \cup B) = P(A) + P(B) - P(A \cap B)$
\item $P(A|B)$
\item $P(B|A)$
Notice: $P(A|B) \neq P(B|A)$\\
Notice: $P(A|B) = P(A)$, $P(B|A) = P(B)$ so $A$ and $B$ are independent.\\
Notice: $P(A \cap B) = P(A)P(B)$
\end{itemize}

\item Let $A$ be the event the outcome is odd and $B$ be the event the outcome is even.\\
Thus $A = \{1,3,5\}$ and $B = \{2,4,,6\}$. Calculate the following:
\begin{itemize}
\item $P(A)$
\item $P(B)$
\item $P(A \cap B)$\\
Notice: $P(A \cap B) = 0$ so $A$ and $B$ are mutually exclusive.
\item $P(A \cup B)$\\
Notice: $P(A \cup B) = P(A) + P(B)$\\
This is true because $A$ and $B$ are mutually exclusive.
\item $P(A|B)$
\item $P(B|A)$
Notice: $P(A|B) \neq P(A)$ so $A$ and $B$ are NOT independent.\\
Notice: $P(A \cap B) = P(A)P(B)$
\end{itemize}
\end{itemize}



\newpage
\subsection{Practice with Definitions}
The following definitions are from Section 3.1 and 3.2 of the OpenStax Introductory Statistics textbook.
\begin{definition*}[Probability]
The probability of any outcome is the long-term relative frequency of that outcome.
\end{definition*}

\begin{definition*}[Independent Events]
Two events A and B are independent if the knowledge that one occurred does not affect the chance the other occurs. Two events are independent if the following are true: $P(A|B) = P(A)$ and $P(B|A) = P(B)$. When two events are independent $P(A \cap B) = P(A)P(B)$.
\end{definition*}
Note you only need to show one of these three conditions are satisfied to show to events are independent.

\begin{definition*}[Mutually Exclusive Events]
A and B are mutually exclusive events if they cannot occur at the same time. This means that A and B do not share any outcomes and $P(A \cap B) = 0.$
\end{definition*}

\begin{exercise*}[Example from Prep]
The distribution of a random sample $S$ of 100 individuals, organized by gender and whether they are right-handed or left-handed is given in the table below.
\begin{itemize}
\item $M$ is the event that the subject is male
\item $F$ is the event that the subject is female
\item $R$ is the event that the subject is right-handed
\item $L$ is the event that the subject is left-handed
\end{itemize}

\begin{table}[h]
\begin{center}
\begin{tabular}{|c|c|c|}
\hline
& Right-handed & Left-handed\\
\hline
Males & 43 & 9\\
\hline
Females & 44 & 4\\
\hline
\end{tabular}
\end{center}
\end{table}


Follow up Questions
\begin{itemize}
\item Are any of these events mutually exclusive? How do you know?
\item Are any of these events independent? How do you know?
\item Are any of these events dependent? How do you know?
\end{itemize}
\end{exercise*}


\newpage
\subsection{Random Variables and Distributions}
\noindent The following definition is from Chapter 4 Introduction in the OpenStax Introductory Statistics textbook.
\begin{definition*}[Random Variable]
A random variable describes the outcomes of a statistical experiment in words.
\end{definition*}
Random variables have both a set of values they can take on and a probability that they take on each value. This information is collected in a distribution function (sometimes called a probability model) for the random variable. When the random variable is discrete, meaning the random variable has only a finite (or countably infinite) number of possible values, then the distribution function function is also called a probability mass function (pmf).

\begin{exercise*}[Example]
Let $R$ be the random variable that represents that value of the roll of a 6-sided die. Thus $R$ could be 1 or $R$ could be 2 or $R$ could be 3 or $R$ could be 4 or $R$ could be 5 or $R$ could be 6. The pmf for $R$ is 
      $$p(r) = 
    \begin{cases}
    \frac{1}{6} & r=1,2,3,4,5,6 \\
    0 & \text{otherwise}
    \end{cases}.$$

\noindent 

\begin{itemize}
\item What is the domain of $p$?
\item What is the range of $p$?
\item Compute $P(R = 3)$.
\item Calculate $P(R \neq 6)$.
\item Find $P(R > 4)$.
\item Given $A$ is the event that $R$ is an odd, calculate $P(A)$.
\item Compute $P(R \leq 2)$.
\item Compute $P(R \leq 7)$.
\item Let's plot this $p(r)$ using R.
\end{itemize}

We compute $P(A)$,
\begin{align*}
P(A) &= P(R=1 \text{ or } R=3 \text{ or } R=5)\\
&= P(R=1) + P(R=3) + P(R=5) \\
&= p(1) + p(3) + p(5) \\
&= \frac{1}{6} + \frac{1}{6} + \frac{1}{6} \\
&= \frac{3}{6} \\
&= \frac{1}{6},
\end{align*} 
since the sets $\{1\}$, $\{3\}$, and $\{5\}$ are disjoint. 
\end{exercise*}


\newpage
\subsection{PREP for Friday}
\begin{exercise*}[PMF and Probability]
Consider the experiment where two 6-sided dice are rolled and we sum the dice. Let $S$ be the random variable that represents the value of the sum of the dice.
\item Find the pmf for $S$.
\item Compute the following:
\begin{itemize}
\item $P(S = 2)$
\item $P(S = 8)$
\item $P(S = 10)$
\item $P(S \leq 3)$
\item $P(S \leq 9)$
\end{itemize}
\end{exercise*}



 
\end{document}