---
title: "MATH 261 Applied Calculus for Data Analysis Syllabus"
output:
  word_document:
    toc: yes
    reference_docx: ../../cs_department/CSE250/250.Syllabus.docx
    keep_md: true
  html_document: 
    toc: yes
    toc_float: 
      collapsed: false
      smooth_scroll: false
params:
  course_id: "M261"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r}
pacman::p_load(tidyverse, googlesheets, knitr, flextable, officer)
big_border = fp_border(color="darkgrey", width = 2)
std_border = fp_border(color="darkgrey", width = 1)
gsheet <- gs_title(params$course_id)
Sys.sleep(6)

dat <- gs_read(gsheet, ws = "kuali") 
kuali <- dat$value
names(kuali) <- dat$type
outcomes <- gs_read(gsheet, ws = "Outcomes") 
grading <- gs_read(gsheet, ws = "Grading") 
weeks <- gs_read(gsheet, ws = "Weeks")
  
```

# Syllabus

## Course Description

*Offering:* `r kuali['offering']`
   
*Pre-Requisite:* `r kuali['prereqs']`

## Course Outcomes

By the end of the semester, each student will be able to:

```{r, results="asis"}
outcomes %>% filter(outcome == "course") %>% .$text %>% str_c("1. ", ., "\n") %>% cat()
```

# Course Details

## Overview

*How does this course relate to other courses?*

`r kuali['syllabus_related_courses']`

*What do I need to be able to do before taking this course?*

`r kuali['syllabus_before']`

*What will I be prepared to do after this course?*

`r kuali['syllabus_todo']`

## Grading:

```{r, results="asis"}
grading %>%
  mutate(bullets = str_c("\n- ", type, " ", percent, "%: ", "(", text, ")")) %>%
   .$bullets %>% cat()
  
```

## Technology and Textbooks

- `r kuali['technology']`
- `r kuali['textbook']`

## Semester Outline

Below is a 14-week outline of the material we will cover.

```{r, results="asis"}
weeks %>%
  mutate(bullets = str_c("\n- **Week ", week, ":** ", description)) %>%
   .$bullets %>% cat()
```

## Detailed topics by week

### Week 1 & 2

- Math Bootcamp
- Installing software

### Week 3

- Derivatives - 1-Dimension
- Motivate 1: Optimization Problems (least squares regression and maximum likelihood)
- Polynomials, Exponential, Log
- Rules: addition, product, chain

### Week 4

- Applications Case Study
    - Min/Max problems - by hand
    - Graph Sketching (increasing/decreasing, local extremums, concavity, inflection) All done on computer to save time
    - 1-Dimensional Hill Climb Case Study - computer

### Week 5

- Derivatives - Theory
- Limits (computer based application)
- Implicit Differentiation
- Higher Order Derivatives

### Week 6

- Applications - Case Study
  
### Week 7

- Derivatives - Multivariate
- Functions of several variables
- Partial Derivatives
- Maxima and Minima
- Optimization with constraints (computer based application) 
- Applications - Case Study
    - Least Squares Regression Case Study - theory by hand, computer with data

### Week 8

- Infinite Series
- Motivate 2: Discrete Probability Distribution (Poisson, Binomial, Geometric)
- Taylor Polynomials
- Taylor Series
- Approximations Using Taylor Series
- Applications - Case Study
    - Moment Generating Function for normal distribution -> mean, variance, skewness, kurtosis (high order derivatives application) 

### Week 9

- Integration
- Motivate 3: Continuous Probability Distributions (Uniform, Exponential, Normal)
- Antiderivatives and Indefinite Integrals
- Integration by substitution
- Integration by parts

### Week 10

- Definite Integral, Riemann Sums
- Fundamental Theorem of Calculus
- Improper Integrals

### Week 11

- Applications - Case Study
- Calculate probability, expectation and variance and cdf from pdf case study
- Relationship between probability densityfunction and cumulative distribution function case study

### Week 12 - 14

- Integration - Multivariate
- Double Integrals
- Applications - Case Study
    - Joint probability distributions, marginal distributions - by computer
- Readings on mathematical models in data science and analytics 

