---
title: "MATH 261 Applied Calculus for Data Analysis"
output:
  word_document:
    toc: yes
    reference_docx: ../../cs_department/CSE250/250.CourseMap.docx
    keep_md: true
  html_document: 
    toc: yes
    toc_float: 
      collapsed: false
      smooth_scroll: false
params:
  course_id: "M261"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r}
pacman::p_load(tidyverse, googlesheets, knitr, flextable, officer)
big_border = fp_border(color="darkgrey", width = 2)
std_border = fp_border(color="darkgrey", width = 1)
gsheet <- gs_title(params$course_id)
dat <- gs_read(gsheet, ws = "kuali") 
kuali <- dat$value
names(kuali) <- dat$type
outcomes <- gs_read(gsheet, ws = "Outcomes") 
grading <- gs_read(gsheet, ws = "Grading") 
  
```


# Overview

## Materials:

There will be `r str_to_lower(kuali["fees"])` student costs.  The course will be `r kuali['credits']` credits with a capacity of `r kuali['enrollment_max']` students.  The textbook is `r kuali["textbook"]`.

## Outcomes:

By the end of the semester, each student will be able to:

```{r, results="asis"}
outcomes %>% filter(outcome == "course") %>% .$text %>% str_c("1. ", ., "\n") %>% cat()
```

## Course Description:

`r kuali['course_description']`

# Course Details

## Syllabus

*Offering:* `r kuali['offering']`

*Pre-Requisite:* `r kuali['prereqs']`

*Grading:*

```{r, results="asis"}
grading %>%
  mutate(bullets = str_c("\n- ", type, " ", percent, "%: ", "(", text, ")")) %>%
   .$bullets %>% cat()
  
```

*Technology*

`r kuali['technology']`

## Kuali

**Summary of request:** `r kuali['summary_request'] `

**Rationale and supporting data for this request:** `r kuali['rationale'] `

**Request impact?** `r kuali['impact_request']`

**Is this request required in any program?** `r kuali['program_required'] `

**Course Map:** `r kuali['coure_map']`

**Syllabus:** `r kuali['syllabus']`

**Request Type:** `r kuali['request_type']`

**Effective Catalog Year:** `r kuali['catalog_year']`

**Subject Code, Course Number:** `r kuali['course_number']`

**Department:** `r kuali['department']`

**Abbreviated Transcript Title (32 characters):** `r kuali['title_abbr_32']`

**Catalog Course Title (100 characters):** `r kuali['title_long_100']`

**Credits:** `r kuali['credits']`

**Grade Type:** `r kuali['grade_type']`

**Contact Hours:** `r kuali['contact_hours']`

**Repeatable Credit:** `r kuali['repeatable']`

**Anticipated Maximum Enrollment:** `r kuali['enrollment_max']`

**Can this course be audited:** `r kuali['audit']`

**Fees:** `r kuali['fees']`

**Prerequisites:** `r kuali['prereqs']`

**Concurrent Requisites:** `r kuali['coreqs']`

**Course Requirements:** `r kuali['requirements_course']`

**Equivalent Courses:** `r kuali['equivalent_course']`

**Course Description for Catalog:** `r kuali['course_description']`

**Objectives:** `r kuali['objectives']`

**Course Syllabus Summary:** 

*How does this course relate to other courses?*

`r kuali['syllabus_related_courses']`

*What do I need to be able to do before taking this course?*

`r kuali['syllabus_before']`

*What will I be prepared to do after this course?*

`r kuali['syllabus_todo']`

