---
output:
  word_document:
    reference_docx: ../../New Course Curriculum Map - Math 283.docx
    keep_md: true
  html_document: 
    toc: yes
    toc_float: 
      collapsed: false
      smooth_scroll: false
params:
  course_id: "M261"
  size_header: 7
  size_body: 10
  size_c1: 9
  height_header: 1.5
  padding: 1
  width_c1: 3
  width_body: .5
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r}
pacman::p_load(tidyverse, googlesheets, knitr, flextable, officer)
big_border = fp_border(color="darkgrey", width = 2)
std_border = fp_border(color="darkgrey", width = 1)
gsheet <- gs_title(params$course_id)
dat <- gs_read(gsheet, ws = "kuali") 
kuali <- dat$value
names(kuali) <- dat$type
outcomes <- gs_read(gsheet, ws = "Outcomes")
Sys.sleep(6)
grading <- gs_read(gsheet, ws = "Grading") 
Sys.sleep(6)
weeks <- gs_read(gsheet, ws = "Weeks") %>%
  mutate(short_names =  str_split_fixed(description, pattern = "\\:", n = 2)[,1])
  
```


##### Course Outcomes Mapped to Program Outcomes

```{r, results="asis"}
short_dat <- tibble(number = 1:4, sname = c("STAT", "PROGRAM", "ANALYZE", "COLLAB.")) %>%
  mutate(sname = factor(sname, levels = sname))

course <- outcomes %>%
  filter(outcome == "course")
program <- outcomes %>%
  filter(outcome == "program") %>%
  select(-outcome, -map) %>%
  left_join(short_dat, by = "number") %>%
  select(sname, program = text, number)


dat <- course %>%
  mutate(short_names = factor(text, levels = unique(text))) %>%
  select(text, map) %>%
  separate_rows(map) %>%
  separate(map, c("number", "ira"), sep = 1) %>%
  select(-number, number = ira, course = text )  %>% 
  mutate(number = as.integer(number)) %>%
  left_join(program, by = "number") %>%
  mutate(number = 1) %>%
  spread(key = sname, value = number, fill = 0) %>%
  select(-program, Course = course) %>%
  group_by(Course) %>%
  summarise_all(sum)

bg_col <- c("black", "white")[dat %>% t(.)  %>% c() %>% as.numeric]

dat %>%
  data.frame() %>%
  flextable() %>%
  fontsize(part = "header", size = params$size_header) %>%
  rotate(rotation = "btlr", part = "header", align = "center") %>%
  padding(padding = 3, part = "all") %>%
  fontsize(part = "body", size = params$size_body) %>%
  fontsize(j =1, size = params$size_c1) %>%
  autofit() %>%
  height(height = 1.1, part = "header") %>%
  border_inner_v(border = std_border) %>%
  align(align = "center", part = "all") %>%
  bg(i = ~ STAT == 1, j = "STAT", bg = "black") %>%
  color(i = ~ STAT == 0, j = "STAT", color = "white") %>%
  bg(i = ~ PROGRAM == 1, j = "PROGRAM", bg = "black") %>%
  color(i = ~ PROGRAM == 0, j = "PROGRAM", color = "white") %>%
  bg(i = ~ ANALYZE == 1, j = "ANALYZE", bg = "black") %>%
  color(i = ~ ANALYZE == 0, j = "ANALYZE", color = "white") %>%
  bg(i = ~ COLLAB. == 1, j = "COLLAB.", bg = "black") %>%
  color(i = ~ COLLAB. == 0, j = "COLLAB.", color = "white") %>%
  width(j = 1, width = 2) %>%
  knit_print()
  

```




##### Mapping from program outcomes to course assessments


```{r, ft.align = "center"}
po <- outcomes %>%
  filter(outcome == "program") %>%
  select(-outcome, -map, outcome = text)

ass <- weeks %>%
  mutate(short_names = factor(short_names, levels = unique(short_names))) %>%
  select(short_names, program) %>%
  separate_rows(program) %>%
  separate(program, c("number", "ira"), sep = 1) %>%
  spread(key = short_names, value = ira) %>%
  filter(!is.na(number)) %>%
  mutate(number = as.integer(number))

dat <- po %>%
  left_join(ass) %>%
  select(-number)%>%
  rename_all(.funs = str_trunc, side = "right", width = 30)

lname <- colnames(dat)
df_name <- dat %>% data.frame() %>% colnames()
colnames(dat) <- df_name

typology <- data.frame(
  col_keys = df_name,
  what = lname,
  stringsAsFactors = FALSE )

dat %>%
  data.frame() %>%
  flextable() %>%
  set_header_df(mapping = typology) %>%
  rotate(rotation = "btlr", part = "header", align = "center") %>%
  padding(padding = params$padding, part = "all") %>%
  fontsize(part = "body", size = params$size_body) %>%
  fontsize(part = "header", size = params$size_header) %>%
  fontsize(j =1, size = params$size_c1) %>%
#  autofit() %>%
  height(height = params$height_header, part = "header") %>%
  border_inner_v(border = std_border) %>%
  align(align = "center", part = "all") %>%
  width(width = params$width_body) %>%
  width(j = 1, width = params$width_c1) %>%
  knit_print()


```

I = outcome introduced; R = outcome reviewed; A = outcome assessed

##### Mapping from university outcomes to assessments

```{r, ft.align = "center"}
po <- outcomes %>%
  filter(outcome == "university") %>%
  select(-outcome, -map, outcome = text)

ass <- weeks %>%
  mutate(short_names = factor(short_names, levels = unique(short_names))) %>%
  select(short_names, university) %>%
  separate_rows(university) %>%
  separate(university, c("number", "ira"), sep = 1) %>%
  spread(key = short_names, value = ira) %>%
  filter(!is.na(number)) %>%
  mutate(number = as.integer(number))

dat <- po %>%
  left_join(ass) %>%
  select(-number) %>%
  rename_all(.funs = str_trunc, side = "right", width = 30)

lname <- colnames(dat)
df_name <- dat %>% data.frame() %>% colnames()
colnames(dat) <- df_name

typology <- data.frame(
  col_keys = df_name,
  what = lname,
  stringsAsFactors = FALSE )

dat %>%
  data.frame() %>%
  flextable() %>%
  set_header_df(mapping = typology) %>%
  rotate(rotation = "btlr", part = "header", align = "center") %>%
  padding(padding = params$padding, part = "all") %>%
  fontsize(part = "body", size = params$size_body) %>%
  fontsize(part = "header", size = params$size_header) %>%
  fontsize(j =1, size = params$size_c1) %>%
#  autofit() %>%
  height(height = params$height_header, part = "header") %>%
  border_inner_v(border = std_border) %>%
  align(align = "center", part = "all") %>%
  width(width = params$width_body) %>%
  width(j = 1, width = params$width_c1) %>%
  knit_print()

```


I = outcome introduced; R = outcome reviewed; A = outcome assessed


##### Mapping from course outcomes to assessments

```{r, ft.align = "center"}
po <- outcomes %>%
  filter(outcome == "course") %>%
  select(-outcome, -map, outcome = text)

ass <- weeks %>%
  mutate(short_names = factor(short_names, levels = unique(short_names))) %>%
  select(short_names, course) %>%
  separate_rows(course) %>%
  separate(course, c("number", "ira"), sep = 1) %>%
  spread(key = short_names, value = ira) %>%
  filter(!is.na(number)) %>%
  mutate(number = as.integer(number))

dat <- po %>%
  left_join(ass) %>%
  select(-number) %>%
  rename_all(.funs = str_trunc, side = "right", width = 30)

lname <- colnames(dat)
df_name <- dat %>% data.frame() %>% colnames()
colnames(dat) <- df_name

typology <- data.frame(
  col_keys = df_name,
  what = lname,
  stringsAsFactors = FALSE )

dat %>%
  data.frame() %>%
  flextable() %>%
  set_header_df(mapping = typology) %>%
  rotate(rotation = "btlr", part = "header", align = "center") %>%
  padding(padding = params$padding, part = "all") %>%
  fontsize(part = "body", size = params$size_body) %>%
  fontsize(part = "header", size = params$size_header) %>%
  fontsize(j =1, size = params$size_c1) %>%
#  autofit() %>%
  height(height = params$height_header, part = "header") %>%
  border_inner_v(border = std_border) %>%
  align(align = "center", part = "all") %>%
  width(width = params$width_body) %>%
  width(j = 1, width = params$width_c1) %>%
  knit_print()


```

I = outcome introduced; R = outcome reviewed; A = outcome assessed

