---
title: "Find Partial Derivatives of a loglikelihood Function (example 2)"
author: "Sister Johnson"
date: "5/25/2021"
output: 
  html_document:
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Consider the model $f_6(t; a_1, a_2) = 100 + a_1t + a_2(1-e^{-0.0003t})$ where $t \geq 0$. The function $f_6$ models the brightness of a lightbulb, measured as a percent of the original intensity of the lightbulb, given the number of hours the lightbulb as been on, $t$. 

In order to fit $f_6$ to a list of 44 measurements, $(t_i, y_i)$ we need to find the first and second partial derivatives of the loglikelihood function for the residuals. Assuming the residuals (or errors) are independent and normally distributed (with mean 0 and standard deviation 1), the loglikelihood function for these errors is $\ell_6(a_1,a_2; \mathbf{t},\mathbf{y}) = 44\ln\left(\frac{1}{\sqrt{2\pi}}\right) + \sum_{i=1}^{44} \left(- \frac{1}{2}\right)(y_i - 100 - a_1t_i - a_2(1-e^{-0.0003t_i}))^2$.

#### Calculating $\frac{\partial \ell_6}{\partial a_1}$
We compute $\frac{\partial \ell_6}{\partial a_1}$ by treating $a_2$ as a constant and differentiate with respect to $a_1$ using the derivative rules.

\begin{align*}
\frac{\partial \ell_6}{\partial a_1}
&= \frac{\partial}{\partial a_1}\left(44\ln\left(\frac{1}{\sqrt{2\pi}}\right)\right) + \sum_{i=1}^{44} \frac{\partial}{\partial a_1}\left(\left(- \frac{1}{2}\right)(y_i - 100 - a_1t_i - a_2(1-e^{-0.0003t_i}))^2\right) &\text{(sum/difference rule)}\\

&= 0 + \sum_{i=1}^{44} \left(- \frac{1}{2}\right)\frac{\partial}{\partial a_1}\left((y_i - 100 - a_1t_i - a_2(1-e^{-0.0003t_i}))^2\right) &\text{(constant and constant multiple rules)}\\

&= \sum_{i=1}^{44} \left(- \frac{1}{2}\right)\left(2(y_i - 100 - a_1t_i - a_2(1-e^{-0.0003t_i}))(-t_i)\right) &\text{(chain rule)}\\

&= \sum_{i=1}^{44} t_i(y_i - 100 - a_1t_i - a_2(1-e^{-0.0003t_i})) &\text{(simplify; multiply $-\frac{1}{2}$, 2, and $-t_i$)}\\
\end{align*}


We can simplify $\frac{\partial \ell_6}{\partial a_1}$ using the properties of sums.

\begin{align*}
\frac{\partial \ell_6}{\partial a_1} &= \sum_{i=1}^{44} t_i(y_i - 100 - a_1t_i - a_2(1-e^{-0.0003t_i})) & \\

&= \sum_{i=1}^{44} t_i(y_i - 100) - a_1t_i^2 - a_2t_i(1-e^{-0.0003t_i}) &\text{(distribution inside the sum)}\\

&= \sum_{i=1}^{44} t_i(y_i - 100) + \sum_{i=1}^{44} -a_1t_i^2 + \sum_{i=1}^{44} -a_2t_i(1-e^{-0.0003t_i}) &\text{(break the sum into three sums)}\\

&= \sum_{i=1}^{44} t_i(y_i - 100) - a_1\sum_{i=1}^{44}t_i^2 - a_2\sum_{i=1}^{44}t_i(1-e^{-0.0003t_i}) &\text{(pull constant multiples out of the sums)}\\
\end{align*}


We see $\frac{\partial \ell_6}{\partial a_1}$ is of the form a constant, subtract a constant multiple of $a_1$, subtract a constant multiple of $a_2$. 
$$\frac{\partial \ell_6}{\partial a_1} = \left(\sum_{i=1}^{44} t_i(y_i - 100)\right) - a_1\left(\sum_{i=1}^{44}t_i^2\right) - a_2\left(\sum_{i=1}^{44}t_i(1-e^{-0.0003t_i})\right)$$

These constants depend on our data and can be computed in R. Let $A = \sum_{i=1}^{44} t_i(y_i - 100) \approx 83738.9$, $B = \sum_{i=1}^{44}t_i^2 \approx 328767530$, and $C = \sum_{i=1}^{44}t_i(1-e^{-0.0003t_i}) \approx 59520.5$.
```{r}
library(data4led)
bulb <- led_bulb(1,seed=2021)

t <- bulb$hours
y <- bulb$percent_intensity

A <- sum((y-100)*t)
A

B <- sum(t^2)
B

C <- sum((1-exp(-0.0003*t))*t)
C

C4.6 <- -sum((y-100)*(1-exp(-0.0003*t)))
C5.6 <- sum((1-exp(-0.0003*t))^2)
```





#### Calculating $\frac{\partial \ell_6}{\partial a_2}$
We compute $\frac{\partial \ell_6}{\partial a_2}$ by treating $a_1$ as a constant and differentiate with respect to $a_2$ using the derivative rules.

\begin{align*}
\frac{\partial \ell_6}{\partial a_2} 
&= \frac{\partial}{\partial a_2}\left(44\ln\left(\frac{1}{\sqrt{2\pi}}\right)\right) + \sum_{i=1}^{44} \frac{\partial}{\partial a_2}\left(\left(- \frac{1}{2}\right)(y_i - 100 - a_1t_i - a_2(1-e^{-0.0003t_i}))^2\right) &\text{(sum/difference rule)}\\

&= 0 + \sum_{i=1}^{44} \left(- \frac{1}{2}\right)\frac{\partial}{\partial a_2}\left((y_i - 100 - a_1t_i - a_2(1-e^{-0.0003t_i}))^2\right) &\text{(constant and constant multiple rules)}\\

&= \sum_{i=1}^{44} \left(- \frac{1}{2}\right)\left(2(y_i - 100 - a_1t_i - a_2(1-e^{-0.0003t_i}))(-(1-e^{-0.0003t_i}))\right) &\text{(chain rule)}\\

&= \sum_{i=1}^{44} (1-e^{-0.0003t_i})(y_i - 100 - a_1t_i - a_2(1-e^{-0.0003t_i})) &\text{(simplify; multiply $-\frac{1}{2}$, 2, and $-(1-e^{-0.0003t_i})$)}\\
\end{align*}


We can simplify $\frac{\partial \ell_6}{\partial a_2}$ using the properties of sums.

\begin{align*}
\frac{\partial \ell_6}{\partial a_2} &= \sum_{i=1}^{44} (1-e^{-0.0003t_i})(y_i - 100 - a_1t_i - a_2(1-e^{-0.0003t_i}))  & \\

&= \sum_{i=1}^{44} (1-e^{-0.0003t_i})(y_i - 100) - a_1t_i(1-e^{-0.0003t_i}) - a_2(1-e^{-0.0003t_i})^2 &\text{(distribution inside the sum)}\\

&= \sum_{i=1}^{44} (1-e^{-0.0003t_i})(y_i - 100) + \sum_{i=1}^{44} -a_1t_i(1-e^{-0.0003t_i}) + \sum_{i=1}^{44} -a_2(1-e^{-0.0003t_i})^2 &\text{(break the sum into three sums)}\\

&= \sum_{i=1}^{44} (1-e^{-0.0003t_i})(y_i - 100) - a_1\sum_{i=1}^{44}t_i(1-e^{-0.0003t_i}) - a_2\sum_{i=1}^{44}(1-e^{-0.0003t_i})^2 &\text{(pull constant multiples out of the sums)}\\
\end{align*}


We see $\frac{\partial \ell_6}{\partial a_2}$ is of the form a constant, subtract a constant multiple of $a_1$, subtract a constant multiple of $a_2$. 
$$\frac{\partial \ell_6}{\partial a_2} = \left(\sum_{i=1}^{44} (1-e^{-0.0003t_i})(y_i - 100)\right) - a_1\left(\sum_{i=1}^{44}t_i(1-e^{-0.0003t_i})\right) - a_2\left(\sum_{i=1}^{44}(1-e^{-0.0003t_i})^2\right)$$

These constants depend on our data and can be computed in R. Let $D = \sum_{i=1}^{44} (1-e^{-0.0003t_i})(y_i - 100) \approx -15.691$, $C = \sum_{i=1}^{44}t_i(1-e^{-0.0003t_i}) \approx 59520.5$, and $E = \sum_{i=1}^{44}(1-e^{-0.0003t_i})^2 \approx 10.998$. Notice that $C$ is a constant in $\frac{\partial \ell_6}{\partial a_2}$ and $\frac{\partial \ell_6}{\partial a_1}$.
```{r}
D <- -sum((y-100)*(1-exp(-0.0003*t)))
D

C <- sum((1-exp(-0.0003*t))*t)
C

E <- sum((1-exp(-0.0003*t))^2)
E
```



We will use the first partials of $\ell_6$ to calculate the second partials of $\ell_6$. We only need to compute $\frac{\partial^2 \ell_6}{\partial a_1^2}$, $\frac{\partial^2 \ell_6}{\partial a_2^2}$ and $\frac{\partial^2 \ell_6}{\partial a_1a_2}$ since the mix partials are equal for $\ell_6$.

#### Calculating $\frac{\partial^2 \ell_6}{\partial a_1^2}$
We compute $\frac{\partial^2 \ell_6}{\partial a_1^2}$ by taking the derivative of $\frac{\partial \ell_6}{\partial a_1}$ with respect to $a_1$.
$$\frac{\partial^2 \ell_6}{\partial a_1^2} = \frac{\partial}{\partial a_1} \left(\left(\sum_{i=1}^{44} t_i(y_i - 100)\right) - a_1\left(\sum_{i=1}^{44}t_i^2\right) - a_2\left(\sum_{i=1}^{44}t_i(1-e^{-0.0003t_i})\right)\right) = 0 - \left(\sum_{i=1}^{44}t_i^2\right) - 0$$
We see $\frac{\partial^2 \ell_6}{\partial a_1^2} = -\sum_{i=1}^{44}t_i^2 \approx -99542$.
```{r}
-B
```




#### Calculating $\frac{\partial^2 \ell_6}{\partial a_2^2}$
We compute $\frac{\partial^2 \ell_6}{\partial a_2^2}$ by taking the derivative of $\frac{\partial \ell_6}{\partial a_2}$ with respect to $a_2$.
$$\frac{\partial^2 \ell_6}{\partial a_2^2} = \frac{\partial}{\partial a_2} \left(\left(\sum_{i=1}^{44} (1-e^{-0.0003t_i})(y_i - 100)\right) - a_1\left(\sum_{i=1}^{44}t_i(1-e^{-0.0003t_i})\right) - a_2\left(\sum_{i=1}^{44}(1-e^{-0.0003t_i})^2\right)\right) = 0 - 0 - \sum_{i=1}^{44}(1-e^{-0.0003t_i})^2$$
We see $\frac{\partial^2 \ell_6}{\partial a_2^2} = - \sum_{i=1}^{44}(1-e^{-0.0003t_i})^2 \approx -10.998$.
```{r}
-E
```



#### Calculating $\frac{\partial^2 \ell_6}{\partial a_1a_2}$
We compute $\frac{\partial^2 \ell_6}{\partial a_1a_2}$ by taking the derivative of $\frac{\partial \ell_6}{\partial a_2}$ with respect to $a_1$.
$$\frac{\partial^2 \ell_6}{\partial a_1a_2} = \frac{\partial}{\partial a_1} \left(\left(\sum_{i=1}^{44} (1-e^{-0.0003t_i})(y_i - 100)\right) - a_1\left(\sum_{i=1}^{44}t_i(1-e^{-0.0003t_i})\right) - a_2\left(\sum_{i=1}^{44}(1-e^{-0.0003t_i})^2\right)\right) = 0 - \sum_{i=1}^{44}t_i(1-e^{-0.0003t_i}) - 0$$
We see $\frac{\partial^2 \ell_6}{\partial a_2^2} = - \sum_{i=1}^{44}t_i(1-e^{-0.0003t_i}) \approx -59520.5$.
```{r}
-C
```

