---
title: "Project 2"
author: "YOUR NAME"
date: "Updated October 15"
output:
  html_document:  
    keep_md: true
    toc: true
    toc_float: true
    code_folding: hide
    fig_height: 6
    fig_width: 12
    fig_align: 'center'
---

```{r, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

```{r load_libraries, include=FALSE}
# Use this R-Chunk to load all your libraries!
  #read in the tidyverse library if you want to use ggplot()
#install.packages("tidyverse") # run this line once in console to get package
#library(tidyverse)
#library(ggplot2)

#devtools::install_github('byuidatascience/data4led') # run this line once in console to get package
library(data4led)
```

```{r load_data}
# Use this R-Chunk to import all your datasets!

#Enter the seed as your birthday MMDD.
bulb <- led_bulb(1,seed=0123)
  #The bulb object is a data frame with measurements for one randomly selected bulb at many time points.
```
<!-- #Color Format -->

##Current Status of Project (Personal Inventory)
INCLUDE this section when submitting the Benchmark Demo & Review.

DELETE this section before turning the Project.
* Which tasks (or portions of the project) are complete?
* Which tasks (or portions of the project) still need to be completed?
* Any questions or confusion?

## BackGround



## Statistic -- A number that summarizes information from data.

```{r, error=TRUE}


```


## Optimize Likelihood Function

```{r, error=TRUE}


```

## Use the Model
  

```{r}


```


## Assume a Different Functional Form for the Model


```{r}


```

## Conclusions


## Reflection
